\begin{thebibliography}{9}
\addcontentsline{toc}{section}{Bibliografie}
\bibitem{boehm}
Boehm, Barry W. (1981). \textit{Software Engineering Economics.} Prentice-Hall. 
\bibitem{anfis}
Jang, J.-S.R. (1993) ANFIS: Adaptive-Network-Based Fuzzy Inference System. \textit{IEEE Transactions On Systems, Man, And Cybernetics}, 23(3), pp. 665-685.
\bibitem{cocomoneuralnets}
Kaushik, A. et al. (2012) COCOMO Estimates Using Neural Networks \textit{I.J. Intelligent Systems and Applications}, 9, pp. 22-8.
\bibitem{anfiscost}
Mokri, F. D. et al. (2016) Software Cost Estimation using Adaptive Neuro Fuzzy Inference System \textit{International Journal of Academic Research in Computer Engineering}, 1(1), pp. 34-39.
\bibitem{promise1}
Promise Software Engineering Repository (2004), \textit{COCOMO Nasa/Software Cost Estimation}. [online] Disponibil la http://promise.site.uottawa.ca/SERepository/datasets/cocomonasa\_v1.arff (30 Aug. 2017)
\bibitem{promise2}
Promise Software Engineering Repository (2004), \textit{COCOMO 81/Software Cost Estimation}. [online] Disponibil la http://promise.site.uottawa.ca/SERepository/datasets/cocomo81.arff (30 Aug. 2017)
\bibitem{klirfuzzy}
Klir, George J. et al. (1995). \textit{Fuzzy Sets and Fuzzy Logic}. Pretince-Hall.
\bibitem{takagisugeno}
Takagi, T. et al. (1983) Derivation of fuzzy control rules from human operator's control actions. \textit{Proc. IFAC Symp. Fuzzy Inform., Knowledge Representation and Decision Analysis}, pp. 55-60.
\bibitem{fcmcluster}
Dunn, J. (1974). A fuzzy relative of the ISODATA process and its use in detecting compact, well separated cluster. \textit{J. Cybernetics}, 3(3), pp. 32-57.
\bibitem{subclustering}
Chiu, S. (1994). Fuzzy Model Identification Based on Cluster Estimation. \textit{Journal of the Intelligent and Fuzzy Systems}, 1(2), pp. 267-278.
\bibitem{statlearn}
Enachescu, D. (2003) \textit{Elements of Statistical Learning. Applications in Data Mining.} Cooperativa Libraria Editrice Universita di Padova.
\end{thebibliography}